Patterns

### 2020-08-28 inst/analysis/patterns.Rmd
more patterns

```{r}
packages <- c(
  "timeSeries",
  "irlba",
  "assertthat",
  "rgenoud",
  "taxize",
  "prodlim",
  "vars" ,
  "betareg"   ,
  "bookdown"  ,
  "R2HTML"   ,
  "withr",
  "processx" ,
  "modeltools"  ,
  "rprojroot"  ,
  "ggplot2",
  "binom",
  "rmarkdown" ,
  "R.methodsS3" ,
  "FactoMineR" ,
  "PerformanceAnalytics"
)
```

```{r}
evals_static <- read_fst(PACKAGE_EVALS_FILE)
```

### parse

```{r}
all_data %>%
  filter(!is.na(parse_args_text))
```

>>>>

```{r}
rnd_packages <- tibble(package=c(
  "timeSeries",
  "irlba",
  "assertthat",
  "rgenoud",
  "taxize",
  "prodlim",
  "data.table" ,
  "betareg"   ,
  "bookdown"  ,
  "R2HTML"   ,
  "withr",
  "processx" ,
  "modeltools"  ,
  "rprojroot"  ,
  "ggplot2",
  "anytime",
  "rmarkdown" ,
  "R.methodsS3" ,
  "FactoMineR" ,
  "PerformanceAnalytics"
))
```

```{r}
evals_static <- read_fst(PACKAGE_EVALS_FILE) %>% as_tibble() %>% semi_join(rnd_packages, by="package")
```

```{r}
overview_table(
  r("Manual packages", nrow(rnd_packages)),
  r("Manual callsites", nrow(evals_static))
)
```
